Sequoidal Categories and Transfinite Games: A Coagebraic Approach to Stateful Objects in Game Semantics\footnote{This work was partially supported by UK EPSRC Grant EP/K037633/1}

### 2017-04-11 round-corner/paper/lipics-v2016-authors/sequoidal.tex
Added missing bracket.

We shall use the following standard pieces of theory about final coalgebras:
\begin{description}
  \item[Lambek's Lemma] $\alpha_A$ is an isomorphism, with inverse given by the anamorphism of the map $\id\sequoid\alpha_A\from A\sequoid\oc A\to A \sequoid (A \sequoid \oc A)$ \cite{Lambek}.  In particular, $\alpha_A$ is a morphism in $\G_s$.  In the general case, we deduce that $\alpha_A$ is a morphism in $\C_s$.  
  \item[Final Sequence] If $\C$ is a category with enough limits and $F$ is an endofunctor on $\C$, we may build up an ordinal indexed sequence of objects and morphisms of $\C$ (that is, a functor $\oppcat{\Ord}\to\C$, where $\Ord$ is the category of ordinals and prefix inclusions:
    \[
      1 \leftarrow F(1) \leftarrow F^2(1) \leftarrow \cdots F^\omega(1) \leftarrow F^{\omega+1}(1) \leftarrow \cdots
      \]
    (by repeatedly applying $F$ and taking limits).  If this sequence stabilizes for any $\delta$ (i.e., if the morphism from $F^{\delta+1}(1)\to F^\delta(1)$ is an isomorphism), then $F^\delta(1)$ is the final coalgebra for $F$ \cite{finalseq}.  
\end{description}

>>>>

We shall use the following standard pieces of theory about final coalgebras:
\begin{description}
  \item[Lambek's Lemma] $\alpha_A$ is an isomorphism, with inverse given by the anamorphism of the map $\id\sequoid\alpha_A\from A\sequoid\oc A\to A \sequoid (A \sequoid \oc A)$ \cite{Lambek}.  In particular, $\alpha_A$ is a morphism in $\G_s$.  In the general case, we deduce that $\alpha_A$ is a morphism in $\C_s$.  
  \item[Final Sequence] If $\C$ is a category with enough limits and $F$ is an endofunctor on $\C$, we may build up an ordinal indexed sequence of objects and morphisms of $\C$ (that is, a functor $\oppcat{\Ord}\to\C$, where $\Ord$ is the category of ordinals and prefix inclusions):
    \[
      1 \leftarrow F(1) \leftarrow F^2(1) \leftarrow \cdots F^\omega(1) \leftarrow F^{\omega+1}(1) \leftarrow \cdots
      \]
    (by repeatedly applying $F$ and taking limits).  If this sequence stabilizes for any $\delta$ (i.e., if the morphism from $F^{\delta+1}(1)\to F^\delta(1)$ is an isomorphism), then $F^\delta(1)$ is the final coalgebra for $F$ \cite{finalseq}.  
\end{description}
